Experiences with Planning for Natural Language Generation

### 2008-06-23 trunk/Papers/experiences/discussion.tex
spellcheck

The most restrictive bottleneck in the two domains we investigated is the
initial grounding step that many modern planners perform. While this may be
a good strategy for traditional planning benchmarks and IPC domains---where
plan length often dominates universe size, and an initial investment into
grounding pays off in saved instantiations during the search---this
approach is less efective in the domains we've considered. As our
experiements have shown, there are natural planning domains in which
relatively short plans must be computed in large universes. For instance,
in the case of the sentence generation domain, it is not unrealistic for
the universe to consist of thousands of domain individuals and tens of
thousands of actions, some of which require three domain individuals as
parameters. The common strategy of splitting the universe over several
types of individuals will not be very effective here.

@@

The recent trend in planning research has (rightfully) focused on the
development of alorithms that control search in sophisticated ways,
resulting in a host of planners that are more powerful and more successful
than their predecessors. Depending on the particular algorithm, however,
these planners often ground out sets of predicates and actions before
starting the search itself, which has a very pronounced effect on domains
such as those described above. Since our domains are not that unusual in
their structure and composition, we hope that the lessons learnt from our
experiences can help improve the performance of current systems. We believe
that such improvements are necessary if planning is to become a more mature
technology that can offer tools to a wider community of users. At the end
of the day, real-world users will care about the \emph{total} runtime of a
planner, and this is more than just the search time.
%We offer our larger problem instances as future challenges for the
%planning community.

>>>>

The most restrictive bottleneck in the two domains we investigated is the
initial grounding step that many modern planners perform. While this may be
a good strategy for traditional planning benchmarks and IPC domains---where
plan length often dominates universe size, and an initial investment into
grounding pays off in saved instantiations during the search---this
approach is less effective in the domains we've considered. As our
experiments have shown, there are natural planning domains in which
relatively short plans must be computed in large universes. For instance,
in the case of the sentence generation domain, it is not unrealistic for
the universe to consist of thousands of domain individuals and tens of
thousands of actions, some of which require three domain individuals as
parameters. The common strategy of splitting the universe over several
types of individuals will not be very effective here.

@@

The recent trend in planning research has (rightfully) focused on the
development of algorithms that control search in sophisticated ways,
resulting in a host of planners that are more powerful and more successful
than their predecessors. Depending on the particular algorithm, however,
these planners often ground out sets of predicates and actions before
starting the search itself, which has a very pronounced effect on domains
such as those described above. Since our domains are not that unusual in
their structure and composition, we hope that the lessons learnt from our
experiences can help improve the performance of current systems. We believe
that such improvements are necessary if planning is to become a more mature
technology that can offer tools to a wider community of users. At the end
of the day, real-world users will care about the \emph{total} runtime of a
planner, and this is more than just the search time.
%We offer our larger problem instances as future challenges for the
%planning community.
